A Gaussian process model of human e\-lect\-ro\-cort\-i\-co\-graph\-ic data

### 2020-03-11 paper/main.tex
minor spellchecking and formatting

The recordings we analyzed from Dataset 1 comprised data collected as the
patients performed a variety of (largely idiosyncratic) tasks throughout each
day's recording session.  That we observed reliable reconstructions  across
patients suggests that the spatial correlations derived from the SuperEEG
algorithm are, to some extent, similar across tasks.  We tested this finding
more directly using Dataset 2.  In Dataset 2, the recordings were limited to
times when each patient was participating in one of two experiments.  Experiment
1 is a random-word list free recall task; Experiment 2 is a categorized list
free recall task (24 patients particpated in both).  We wondered whether a
correlation model learned from data from one experiment might yield good
predictions of data from the other experiment.  Further, we wondered about the
extent to which it might be beneficial or harmful to combine data across tasks.

@@

\section*{Author Information}
Reprints and permissions information is available
at www.nature.com/reprints.  The authors declare no competing financial
interests.  Readers are welcome to comment on the online version of the paper.
Publisher's note: Springer Nature remains neutral with regard to jurisdictional
claims in published maps and institutional affiliations.  Correspondence and
requests for materials should be addressed to J.R.M.
(jeremy.r.manning@dartmouth.edu).

\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}

\clearpage

>>>>

The recordings we analyzed from Dataset 1 comprised data collected as the
patients performed a variety of (largely idiosyncratic) tasks throughout each
day's recording session.  That we observed reliable reconstructions  across
patients suggests that the spatial correlations derived from the SuperEEG
algorithm are, to some extent, similar across tasks.  We tested this finding
more directly using Dataset 2.  In Dataset 2, the recordings were limited to
times when each patient was participating in one of two experiments.  Experiment
1 is a random-word list free recall task; Experiment 2 is a categorized list
free recall task (24 patients participated in both).  We wondered whether a
correlation model learned from data from one experiment might yield good
predictions of data from the other experiment.  Further, we wondered about the
extent to which it might be beneficial or harmful to combine data across tasks.

@@

%\clearpage
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
